\problem Let $x$ be a nilpotent element of a ring $A$. Show that $1 + x$ is a unit of $A$.
Deduce that the sum of a nilpotent element and a unit is a unit.

\begin{proof}
    Let $x \in A$ be nilpotent.
    Then, $x \in \nilradical \subset \jacobsonradical$, so for all $y \in A$, $1- xy$ is a unit in $A$.
    In particular, $1 + x = 1 - x(-1)$ is a unit in $A$, as claimed.

    Let now $y$ be a unit of $A$.
    Then, $x + y = y(y^{-1}x + 1)$.
    As $x \in \nilradical$, $y^{-1}x \in \nilradical$ so that by the above, $y^{-1}x + 1$ is a unit in $A$.
    It follows that as a product of units in $A$, $x + y$ is also a unit in $A$.
\end{proof}

\problem Let $f = a_0 + a_1x + \cdots + a_nx^n \in A[X]$. Prove that:
\begin{enumerate}[i)]
    \item $f$ is a unit in $A[X] \Leftrightarrow a_0$ is a unit in $A$ and $a_1,\dots, a_n$ are nilpotent.
        \begin{proof}
            If $a_0$ is a unit and $a_1,\cdots, a_n$ are nilpotent, then $a_1x + \cdots + a_nx^n$ is nilpotent.
            Hence, $f = a_0 + (a_1x + \cdots + a_nx^n)$ is the sum of a unit and a nilpotent element, so $f$ is a unit.

            Conversely, suppose $f$ is a unit and let $g = b_0 + \cdots + b_mx^m$ be the inverse of $f$.
            We'll show by induction on $r$ that $a_n^{r+1}b_{m-r} = 0$ from which the proof will follow.
            First, put $$c_k = \sum_{i+j = k}a_ib_j \hspace{1cm}(k = 1, \cdots, m+n)$$
            so \[
                fg = \sum_{i=0}^{m+n}c_ix^i.
            \]
            Since $fg = 1$, it follows that each $c_i = 0$ for $i > 0$ and that $c_0 = a_0b_0 = 1$.
            In particular, $a_0$ is a unit and if $r = 0$, then $a_n^{r+1}b_{m-r} = a_nb_m = c_{m+n} = 0$. 
            Suppose now that $a_n^{s+1}b_{m-s} = 0$ for all $1 \leq s < r$.
            By induction, \[
                a_n^rg = a_n^r(b_0 + \cdots + b_mx^m) = a_n^rb_0 + \cdots + a_n^rb_{m-r}
            \]
            so \[
                a_n^{r+1} = a_n^{r+1}fg = a_nfa_n^rg = a_n\sum_{i=0}^{n+(m-r)}(\sum_{j+k = i}a_ja_n^rb_k)x = a_0a_n^rb_0 + \cdots + a_na_n^rb_{m-r}x^{n+m-r},
            \]
            whence $a_n^{r+1}b_{m-r} = 0$.
            Thus, $a_n^{m+1}b_0 = 0$, so since $b_0$ is a unit, $a_n$ is nilpotent.

            It follows that $f - a_nx^n = a_0 + \cdots + a_{n-1}x^{n-1}$ is the sum of a unit and a nilpotent element, hence a unit.
            Thus, $a_{n-1}$ is nilpotent, and applying this argument recursively, we get that $a_n, \cdots, a_1$ are nilpotent.
        \end{proof}

        \begin{proof}[Alternative Proof]
            Note that when $A$ is an integral domain, $f$ being a unit means that $a_0$ is a unit and that $a_1, \cdots, a_n = 0$.
            Let $\mathfrak{p}$ be a prime ideal of $A$ and consider the image $\tilde{f}$ of $f$ under the map $A[x] \to A/\mathfrak{p}[x]$.
            One can easily verify that this map is a ring homomorphism and so $\tilde{f}$ is a unit in $A/\frak{p}[x]$.
            Since $\frak{p}$ is prime, $A/\frak{p}$ is an integral domain and by the above remark, $a_1, \cdots, a_n \equiv 0 \mod \frak p$.
            Hence, $a_1, \cdots, a_n \in \frak p$.
            Since $\frak p$ was an arbitrary prime ideal, it follows that $a_1, \cdots, a_n \in \bigcap_{\frak p}\frak p = \nilradical$.
            That $a_0$ is a unit follows from it being the constant term of $f$.
        \end{proof}
        
        \item $f$ is nilpotent $\Leftrightarrow$ $a_0, a_1, \cdots, a_n$ are nilpotent.
            \begin{proof}
                If $a_0, \cdots, a_n$ are nilpotent, then $f$ is a sum of nilpotents, hence is nilpotent.
                If $f$ is nilpotent, then $xf$ is nilpotent. Hence, $1 + xf = 1 + a_0x + \cdots + a_nx^{n+1}$ is a unit.
                It follows from (i) that $a_0, \cdots, a_n$ are nilpotent.
            \end{proof}
\end{enumerate}

\setcounter{problem}{3}
\problem In the ring $A[x]$, the Jacobson radical is equal to the nilradical.
\begin{proof}
    Since every maximal ideal is prime, $\nilradical \subset \jacobsonradical$.
    Given $f = a_0 + \cdots + a_nx^n \in \jacobsonradical$, we know that $1-yf$ is a unit for all $y \in A[x]$.
    In particular, $1 + xf = 1 + a_0x + \cdots + a_{n}x^{n+1}$ is a unit, so by 2(i), every $a_i$ is nilpotent.
    Then, by 2(ii), $f$ is nilpotent.
\end{proof}

\setcounter{problem}{5}

\problem A ring $A$ is such that every ideal not contained in the nilradical contains a nonzero idempotent (that is, an element $e$ such that $e^2 = e \not= 0$). Prove that the nilradical and Jacobson radical of $A$ are equal.
\begin{proof}
    The Jacobson radical $\jacobsonradical$ of $A$ is an ideal of $A$ containing $\nilradical$.
    If the containment were proper, then by assumption, there is a nonzero element $e \in \jacobsonradical$ such that $e^2 = e$.
    Then, $e(e-1) = 0$. But, $e$ being in $\jacobsonradical$ means that $e-1$ is a unit in $A$, whence $e(e-1) = 0$ implies $e = 0$.
    Contradiction!
\end{proof}

\problem Let $A$ be a ring in which every element $x$ satisfies $x^n = x$ for some $n > 1$ (depending on $x$).
Show that every prime ideal in $A$ is maximal.

\begin{proof}
    Let $\frak{p} \ideal A$ be prime.
    We will show that the ring $A/\frak{p}$ is a field.
    Indeed, as $\frak{p}$ is prime, $A/\frak{p}$ is already an integral domain.
    Thus, it suffices to show that every nonzero $x + \frak{p}$ in $A/\frak{p}$ is invertible.
    To this end, let $x + \frak{p} \in A/\frak{p}$, not zero, be arbitrary.
    By assumption, there is an integer $n > 1$ so that $x^n = x$, or $x(x^{n-1} - 1) = 0$.
    Hence, $(x + \frak{p})(x^{n-1} -1  + \frak{p}) = \frak{p}$.
    Since $x + \frak{p}$ is not zero and $A/\frak{p}$ is an ID, it follows that $x^{n-1} - 1 + \frak{p} = \frak{p}$.
    Hence, $x^{n-1} + \frak{p} = 1 + \frak{p}$ so that $x + \frak{p}$ is a invertible.
    It follows that $A/\frak{p}$ is a field, whence $\frak{p} \ideal A$ is maximal.
\end{proof}

\problem Let $A$ be a ring $\not=\zero$. Show that the set of prime ideals of $A$ has minimal elements with respect to inclusion.
\begin{proof}
    Let $\Sigma$ be the set of prime ideals of $A$ ordered by inclusion.
    We will use Zorn's Lemma to show that every chain in $\Sigma$ has a lower bound, whence $\Sigma$ has a minimal element.
    Indeed, $\Sigma$ is nonempty since (by Zorn's Lemma) $A$ contains a maximal ideal.
    Let now $\{\frak{p}_\iota\}_{\iota \in I}$ be a chain in $\Sigma$ indexed by the set $I$ and let $\frak{p} = \bigcap_{\iota \in I} \frak{p}_\iota$.
    We claim that $\frak{p} \in \Sigma$.
    First, that $\frak{p}$ is an ideal of $A$ follows from $\frak{p}$ being an intersection of ideals.
    To show that $\frak{p}$ is prime, let $xy \in \frak{p}$ be arbitrary.
    Then, $xy \in \frak{p}_\iota$ for all $\iota \in I$.
    Suppose that $x\notin \frak{p}$ and $y \notin \frak{p}$.
    Then there are indices $\alpha, \beta \in I$ such that $x \notin \frak{p}_\alpha$ and $y\notin \frak{p}_\beta$.
    Since $\{\frak{p}_\iota\}$ is a chain, either $\frak{p}_\alpha \subseteq \frak{p}_\beta$ or $\frak{p}_\beta \subseteq \frak{p}_\alpha$.
    In either case, the smaller ideal contains neither $x$ nor $y$, but does contain $xy$. Contradiction!
    Thus, either $x\in \frak{p}$ or $y \in \frak{p}$. Hence, $\frak{p} \in \Sigma$.

    Of course, $\frak{p} \subseteq \frak{p}_\iota$ for every $\iota \in I$ so that $\frak{p}$ is a lower bound for $\{\frak{p}_\iota\}$.
    It follows by Zorn's Lemma that $\Sigma$ contains a minimal element, as claimed.
\end{proof}